\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-01 arch.tex
some initials text on last subsection

\subsubsection{Intertwining synchronization and execution }
\label{sec:arch:intertwine}

>>>>

\subsubsection{Intertwining synchronization and execution}
\label{sec:arch:intertwine}

A core aspect of this reactor is that it takes advantage of the
specific sequencing enforced by the T-REX architecture along with the
fact that only one $plan$ structure is maintined in the reactor and
shared between synchronization and planning to allow these two processes
to not only be interleaved but impact each other through the way they
manipulate this plan.
